A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-07 paper.tex
merge

\brian{Cite Getzler \cite{GetzlerBracket}}

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

@@

There is a corollary of this proposition obtained by iterating the procedure. 
We will only use a single iteration.

\begin{cor} \label{cor: quad}
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
\]
whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
Suppose further that the local functional
\[
S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i} 
\]
satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
\[
E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
\]
and
\[
S' = S_0 + \int \phi_1 \psi_1^* - S''
\]
where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
\end{cor}
\begin{proof}
%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
We begin by making the following change of coordinates on the BV fields:
\begin{align*}
\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
\end{align*}
with $\phi_1, \psi_1$ left fixed. 
This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
Further, in the new coordinates, the action takes the form
\[
S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
\]
\end{proof}

@@

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

>>>>

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.

We explain how to define the BV bracket in our context.  
First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

@@

%There is a corollary of this proposition obtained by iterating the procedure. 
%We will only use a single iteration. 
%
%\begin{cor} \label{cor: quad}
%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
%\[
%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
%\]
%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
%Suppose further that the local functional
%\[
%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i} 
%\]
%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
%\[
%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
%\]
%and
%\[
%S' = S_0 + \int \phi_1 \psi_1^* - S''
%\]
%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
%\end{cor}
%\begin{proof}
%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
%We begin by making the following change of coordinates on the BV fields:
%\begin{align*}
%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
%\end{align*}
%with $\phi_1, \psi_1$ left fixed. 
%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
%Further, in the new coordinates, the action takes the form
%\[
%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
%\]
%\end{proof}

@@

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{s,t} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varsigma\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.
